---
title: "Probability distribution"
author: "hunglin"
date: "1/5/2020"
output: html_document
---
## Usage
+ dnorm(x, mean = 0, sd = 1, log = FALSE)
+ pnorm(q, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
+ qnorm(p, mean = 0, sd = 1, lower.tail = TRUE, log.p = FALSE)
+ rnorm(n, mean = 0, sd = 1)  

## Arguments
+ x, q	vector of quantiles.  
+ p	 vector of probabilities.
+ n	 number of observations. If length(n) > 1, the length is taken to be the number required.  
+ mean	vector of means.
+ sd	vector of standard deviations.
+ log, log.p	logical; if TRUE, probabilities p are given as log(p).  
+ lower.tail	logical; if TRUE (default), probabilities are P[X ≤ x] otherwise, P[X > x].

***

```{r basic}
# extract 10 values from 0-1 standard normal distribution
rnorm_10 <- rnorm(n = 10,mean = 20, sd = 5)
print(rnorm_10)

dnorm(rnorm_10) # the density of the values
#qnorm()

qnorm(c(0.05, 0.95, 0.05/2, 0.95/2, 0.5)) # z score
pnorm(qnorm(c(0.05, 0.95, 0.05/2, 0.95/2, 0.5)) )
```

## Plot a normal distribution

make the values for normal distribution
```{r}
randnorm <- rnorm(10000) # make 10000 values
randdensity <- dnorm(randnorm) # a probability of a value 
library(ggplot2)
ggplot(data.frame(x = randnorm, y = randdensity)) + aes(x = x, y = y) + geom_point() + 
  labs(x = "Random Normal Variables", y = "Density")
randprob <- pnorm(randnorm)
randquan <- qnorm(randprob)
ggplot(data.frame(x = randprob, y = randquan)) + aes(x = x, y = y) + geom_point() + 
  labs(x = "Probability", y = "Quantile")
```


